Naming Anonymous JavaScript Functions

### 2011-04-14 papers/splash-wavefront2011/sigplanconf-template.tex
two correction from salman

\section{Discussion}
Overall the Function-Object Consumption approach dramatically improves reduces the number of functions that a development tool cannot name for a developer.  By looking at the examples and comparing the algorithms, the names selected by FOC will be the same as the one's selected by  Firebug's {\small \texttt{guessFunctionName()}} when that function gives reasonable results. In other cases FOC will give a more useful name including many cases where the current Firebug approach fails.

@@

H{\o}st and {\O}stvold \cite{Host} attempted to find and fix inappropriate function names in Java programs. Their approach employs rules extracted from a big corpus of Java projects to recognize buggy names. To fix a name a list of candidate names are constructed and ranked, the the name with highest rank is proposed for the replacement. This approach assumes that the function is already named and constructs the names based on the function internal structure. In contrast, our approach construct the function name by analyzing the function context.

>>>>

\section{Discussion}
Overall the Function-Object Consumption approach dramatically reduces the number of functions that a development tool cannot name for a developer.  By looking at the examples and comparing the algorithms, the names selected by FOC will be the same as the one's selected by  Firebug's {\small \texttt{guessFunctionName()}} when that function gives reasonable results. In other cases FOC will give a more useful name including many cases where the current Firebug approach fails.

@@

H{\o}st and {\O}stvold \cite{Host} attempted to find and fix inappropriate function names in Java programs. Their approach employs rules extracted from a large corpus of Java projects to recognize buggy names. To fix a name a list of candidate names are constructed and ranked, the the name with highest rank is proposed for the replacement. This approach assumes that the function is already named and constructs the names based on the function internal structure. In contrast, our approach construct the function name by analyzing the function context.
